A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-12-09 doc/review-acom/stokes-eig.tex
small updates

  $$ E_\rho = \left \{ z: \left(\frac{2\Re z}{\rho+1/\rho}
  \right )^2 + \left(\frac{2\Im z}{\rho-1/\rho}
  \right )^2  = 1 \right \} \; .$$
  Let $T$ be the linear transformation that
  maps $[a,b]$ to $[-1,1]$.
  We then keep only the roots such that
  $T(k_\cheb)$ is contained in the Bernstein
  ellipse $E_\rho$ with $\rho = 1+\sqrt{\epscheb}$.
  While it is still possible to obtain two copies
  of a root if it is almost equal to an
  endpoint of one of the subintervals,
  this was not observed in our experiments.
}

@@

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
There were 103 total roots: 21 were removed because
the imaginary part was too large and 6 pairs were found
with values within $\sqrt{\epscheb}$ of each other.
%
For these 6 pairs, none represented two distinct
eigenvalues or a double root.
%
This leaves 76 roots in the range $0\leq k \leq 9$.
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2i\cSk^N-2\cW^N$ for {\color{red}$k$ equal to the real part of}
each of these roots in
\cref{subfig:many_inclusions_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:many_inclusions_gallery}.
%
In the vorticity plots, we observe a different type of
localization property than that seen in the barbell,
with many of the eigenfunctions
approximately supported in a small, connected subset
of the domain. This is consistent with other studies
\cite{filoche2009strong,lindsay2018boundary}.

>>>>

  $$ E_\rho = \left \{ z: \left(\frac{2\Re z}{\rho+1/\rho}
  \right )^2 + \left(\frac{2\Im z}{\rho-1/\rho}
  \right )^2  = 1 \right \} \; .$$
  Let $T$ be the linear transformation that
  maps $[a,b]$ to $[-1,1]$.
  We then keep only the roots such that
  $T(k_\cheb)$ is contained in the Bernstein
  ellipse $E_\rho$ with $\rho = 1+10\sqrt{\epscheb}$.
  While it is still possible to obtain two copies
  of a root if it is almost equal to an
  endpoint of one of the subintervals,
  this was not observed in our experiments.
}

@@

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
{\color{red} There were 76 roots in the range $0 \leq k \leq 9$.}
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2i\cSk^N-2\cW^N$ for {\color{red}$k$ equal to the real part of}
each of these roots in
\cref{subfig:many_inclusions_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:many_inclusions_gallery}.
%
In the vorticity plots, we observe a different type of
localization property than that seen in the barbell,
with many of the eigenfunctions
approximately supported in a small, connected subset
of the domain. This is consistent with other studies
\cite{filoche2009strong,lindsay2018boundary}.
